### 2021-09-06 sections/appendix/descrete_event_simulation/main.tex
Include code Tutorial
Modify appendix based on Diataxis framework (Tutorial-Howto-Reference-
Explanation). This commit adds the initial draft of the Tutorial part.

The same performance measures described in sections 
\ref{sec:waiting_time}, \ref{sec:blocking_time} and 
\ref{sec:proportion_within_target} can also be calculated using the DES model.
The simulation can be ran a number of times to eliminate stochasticity and the
outcomes of the two methods can be directly comparable. 
% TODO Add more documentation (instructions on how to use code)

>>>>

The same performance measures described in sections 
\ref{sec:waiting_time}, \ref{sec:blocking_time} and 
\ref{sec:proportion_within_target} can also be calculated using the DES model.
The simulation can be ran a number of times to eliminate stochasticity and the
outcomes of the two methods can be directly comparable.

\subsection{Tutorial: building the DES model}

The DES model is constructed in a generic way that so that it can be used for
any queueing system with two waiting spaces and two types of individuals.
For instance, consider a queueing system with the following parameters, as 
described in section~\ref{sec:queueing_model}:

\begin{multicols}{4}
    \begin{itemize}
        \item \( \lambda_1 = 2 \)
        \item \( \lambda_2 = 3 \)
        \columnbreak
        \item \( \mu = 1 \)
        \item \( C = 6 \)
        \columnbreak
        \item \( T = 10 \)
        \item \( N = 20 \)
        \columnbreak
        \item \( M = 10 \)
    \end{itemize}
\end{multicols}

\begin{figure}[h]
    \centering
    \begin{tikzpicture}[>=stealth, scale=0.8],
        % the rectangle of parking queue
        \draw (0,0) -- ++(3cm,0) -- ++(0,-1.5cm) -- ++(-3cm,0);
        % the vertical lines of parking queue
        \foreach \i in {1,...,4, 7.1}
            \draw (3cm-\i*12pt,0) -- +(0,-1.5cm);

        % The label above Queue 1 -> M
        \node[anchor=north] at (1.5cm, 1cm) {\( 
            \overbrace{\qquad \qquad \qquad \qquad}^{10} 
        \)};

        % the rectangle in Queue 2
        \draw (5,1.25) -- ++(2cm,0) -- ++(0,-1.5cm) -- ++(-2cm,0);
        % the vertical lines in Queue 2
        \foreach \i in {1,...,4, 5.7}
            \draw (7cm-\i*10pt,1.25) -- +(0,-1.5cm);
        % The two vertical lines at the very start of Queue 2 
        \draw (7cm-54pt,1.2) -- +(0,-0.5cm);
        \draw (7cm-54pt,0.3) -- +(0,-0.5cm);        
        \draw (7cm-51pt,1.1) -- +(0,-0.4cm);
        \draw (7cm-51pt,0.3) -- +(0,-0.4cm);

        % The label between the lines for T
        \node[anchor=north] at (5.19, 0.78 cm) {\small{\( 10 \)}};

        % The label above Queue 2 -> N
        \node[anchor=north] at (6.6cm, 2.2cm) {\(
            \overbrace{\qquad \qquad \qquad \qquad}^{20}
        \)};

        % the circle in Queue 2
        \draw (7.75,0.5) circle [radius=0.75cm] node {\(6\)};

        % Arrow line from Queue 2 outside
        \draw[->] (8.5,0.525) -- +(20pt,0);

        % Line from lambda_2 to Queue 1
        \draw[<-] (-0.3,-0.75) -- +(-40pt,0) node[left] {\( 3 \)};

        % Lines after Parking queue
        \draw[-] (3,-0.75) -- +(34pt,0);
        \draw (4.2, 0.525) -- (4.2, -0.75);

        % Lines for lambda_1 arrivals
        \draw (4.2, 1.8) -- +(-169.5pt,0) node[left] {\( 2 \)};
        \draw (4.2, 1.8) -- (4.2, 0.525);

        % Line from both individuals to Queue 2
        \draw[->] (4.2, 0.525) -- (4.8, 0.525);  
    \end{tikzpicture}
    \caption{A diagrammatic representation of the queueing model example}
    \label{fig:diagram_of_queueing_system_appendix_example}
\end{figure}

This model will be studied by using  
\lstinline[style=pystyle]{ambulance_game}.
Install the created library in your python environment, by running the 
following command in the command line:
\begin{lstlisting}[language=bash, style=terminalstyle]
    $ pip install ambulance_game
\end{lstlisting}

Having installed the package, the following code can be used to simulate the 
queueing system defined earlier and get all the data records for a single run.

\begin{lstlisting}[style=pystyle]

    >>> import ambulance_game as abg
    >>> Simulation = abg.simulation.simulate_model(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ... )
    >>> all_records = Simulation.get_all_records()
    >>> all_records[3]
    Record(id_number=1, customer_class=0, node=2, arrival_date=0.4728763843239206, waiting_time=0.0, service_start_date=0.4728763843239206, service_time=0.5457131455415929, service_end_date=1.0185895298655134, time_blocked=0.0, exit_date=1.0185895298655134, destination=-1, queue_size_at_arrival=0, queue_size_at_departure=4)
\end{lstlisting}

The above block code outputs the fourth individual record from the simulation
object.
The simulation object can be used to view the every event that occurred in the 
simulation 
The data records can then be used to get overall performance measures about the
constructed queueing model.
The overall waiting time that individuals wait in waiting zone 1 can be acquired 
by running:

\begin{lstlisting}[style=pystyle]
    >>> import numpy as np
    >>> mean_wait = np.mean(
    ...    [record.waiting_time for record in all_records if record.node == 2]
    ... )
    0.2246928220731305
\end{lstlisting}

This value is the average waiting time of all the customers in the system for a
single run. 
By nature, discrete event simulation can output different results for different
runs of the same set of parameters.
This stochasticity can be reduced by running the simulation multiple times 
and then getting the mean waiting time from all the runs.

\begin{lstlisting}[style=pystyle]
    >>> all_simulations = abg.simulation.get_multiple_runs_results(
    ...     lambda_1=3,
    ...     lambda_2=2,
    ...     mu=1,
    ...     num_of_servers=6,
    ...     threshold=10,
    ...     system_capacity=20,
    ...     buffer_capacity=10,
    ...     seed_num=0,
    ...     num_of_trials=10,
    ... )
    >>> mean_wait = np.mean(
    ...     [np.mean(w.waiting_times) for w in all_simulations]
    ... )
    0.35037759808989827
\end{lstlisting}

\subsection{How-to guide}

\subsection{Reference}

\subsection{Explanation}
